Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
PULL

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.

>>>>

To summarize, we first reduced the number of constraints from every possible
interval $[t_1, t_2]$ to the intervals where $t_1$ is an arrival time and
$t_2$ is a deadline in $[t_d, t_d + H]$ if $t_d$ exists, or in
$[O_{max}, O_{max} + 2H]$ otherwise. This set of constraints is a
correct description of the C-Space, but it is not efficient. Redundant
contraints are removed through a linear integer approach.
